Dark Control:\\ A Unified Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2017-04-06 paper/paper.tex
fixup
more

Computing an optimal policy then corresponds to finding the parameters $\theta^Q_{k+1}$ which minimize the following mean-squared loss function
\begin{equation}
  \mathcal L(\theta^Q_{k+1})
  % = \mathbb E_{(s, a, r, s') \sim \mathcal U(D)}[(Q(s, a|\theta^Q) - Q(s',a'|\theta^Q_{k+1}))^2]
  = \mathbb E_{(s, a, r, s') \sim \mathcal U(D)}\left[\frac{1}{2}(Q(s, a|\theta^Q_{k+1}) - y)^2\right],
  \label{eq:oracle}
\end{equation}
where
$ y: = r + \gamma \max_{a' \in \mathcal A} Q(s', a'|\theta^Q_k) = r + \gamma Q(s', \pi(s')|\theta^Q_k)$ is the prediction target.
% While $y_t$ is also dependent on $\theta^Q$, this is typically ignored.
For instance, a general linear model with a kernel $\phi$ would be of the
form
$${Q}(s, a|\theta^Q) = \phi(s,a)^T\theta^Q.$$
$\phi(s,a)$ would represent a high-level hand-crafted representation in an
appropriate form of the state-action pairs $(s,a)$,
as proposed by \citep{songNIPS2016}.
%  and Parr et al. 2003 (JMLR)].
A recently proposed, practically successful alternative approach
\citep{mnih2015,silver2016mastering} is to learn this
representation using a deep neural network, leading to the so-called \textit{Deep Q-learning} family of methods which
likely are state-of-the-art in RL.
The set of $\theta^Q$ parameters that instantiate the nonlinear interactions
between layers of the artifical neural network
may find a neurobiological correspondence in the adaptive strengths of axonal
connections between neurons from the different levels
of the neural processing hierarchy
\citep{mesulam1998sensation, taylor2015global}.

@@

\begin{figure}[!tb]
  \centering
  \includegraphics[width=.8\linewidth]{vae.pdf}
  \caption{Variational autoencoders...}
  \label{fig:vae}
\end{figure}

\paragraph{Solution: The reparametrization trick.}
\begin{itemize}
\item Choose $\epsilon \sim p_{\text{noise}}$ (noise distribution, independent of $\W^R$!)
\item Set $\z = g(\W^{R}, \x, \epsilon)$, where $g$ is an appropriate class $\mathcal C^1$ function
  \begin{itemize}
  \item results in a sample $\z \sim p_R(.|\x)$, from the correct
    posterior
    \end{itemize}
\end{itemize}
The mapping $g$ should be taught of as a ``blurring'' function which produces noisy versions $\z$,
called \textit{sensations}, of the true world state $\x$.
The result is a scheme for training DBNs via good-old backprop!
Refer to Fig. \ref{fig:vae}. Some examples of the reparametrization trick for a number of
choices of the posterior distribution are given in Tab. \ref{tab:rptrick}.

>>>>

Computing an optimal policy then corresponds to finding the parameters $\theta^Q_{k+1}$ which minimize the following mean-squared loss function
\begin{equation}
  \mathcal L(\theta^Q_{k+1})
  % = \mathbb E_{(s, a, r, s') \sim \mathcal U(D)}[(Q(s, a|\theta^Q) - Q(s',a'|\theta^Q_{k+1}))^2]
  = \mathbb E_{(s, a, r, s') \sim \mathcal U(D)}\left[\frac{1}{2}(Q(s, a|\theta^Q_{k+1}) - y)^2\right],
  \label{eq:oracle}
\end{equation}
where
$ y: = r + \gamma \max_{a' \in \mathcal A} Q(s', a'|\theta^Q_k) = r + \gamma Q(s', \pi(s')|\theta^Q_k)$ is the prediction target.
% While $y_t$ is also dependent on $\theta^Q$, this is typically ignored.
For instance, a general linear model with a kernel $\phi$ would be of the
form
$${Q}(s, a|\theta^Q) = \phi(s,a)^T\theta^Q.$$
$\phi(s,a)$ would represent a high-level hand-crafted representation of the state-action pairs
$(s,a)$, as proposed by \citep{songNIPS2016}.
%  and Parr et al. 2003 (JMLR)].
A recently proposed, practically successful alternative approach
\citep{mnih2015,silver2016mastering} is to learn this
representation using a deep neural network, leading to the so-called \textit{Deep Q-learning} family of methods which
likely are state-of-the-art in RL.
The set of $\theta^Q$ parameters that instantiate the nonlinear interactions
between layers of the artifical neural network
may find a neurobiological correspondence in the adaptive strengths of axonal
connections between neurons from the different levels
of the neural processing hierarchy
\citep{mesulam1998sensation, taylor2015global}.

@@

% \begin{figure}[!tb]
%   \centering
%   \includegraphics[width=.8\linewidth]{vae.pdf}
%   \caption{Variational autoencoders...}
%   \label{fig:vae}
% \end{figure}

\paragraph{Solution: The reparametrization trick.}
\begin{itemize}
\item Choose $\epsilon \sim p_{\text{noise}}$ (noise distribution, independent of $\W^R$!)
\item Set $\z = g(\W^{R}, \x, \epsilon)$, where $g$ is an appropriate class $\mathcal C^1$ function
  \begin{itemize}
  \item results in a sample $\z \sim p_R(.|\x)$, from the correct
    posterior
    \end{itemize}
\end{itemize}
The mapping $g$ should be taught of as a ``blurring'' function which produces noisy versions $\z$,
called \textit{sensations}, of the true world state $\x$.
The result is a scheme for training DBNs via good-old backprop!
Refer to Fig. vae.pdf.
% \ref{fig:vae}.
Some examples of the reparametrization trick for a number of
choices of the posterior distribution are given in Tab. \ref{tab:rptrick}.
